### 2013-02-07 04-revise-math/X5-ReviseMath.tex
revise

\begin{center}
\large
\textbf{The Largest Prime}
\end{center}
\normalsize
\noindent
Suppose that there were a largest prime number $p_i$. 
Then consider the product $\prod_{j=0}^{p_i-1} \; p_i-j$. 
Then $\left( \prod_{j=0}^{p_i-1} \; p_i - j \right) \,+\,1$ 
cannot be divided evenly by any of the numbers
up to $p_i$, $2,3,4,\ldots,p_i$ because each of these divides the left
factor evenly, but not the right factor, hence not their sum.
(Recall that if $a_1$ divides $a_2$ and $a_2=a_3+a_4$ then if $a_1$
divides $a_3$, it will also divide $a_4$.)  
Since we are assuming
$p_i$ is the largest prime, $\left(\prod_{j=0}^{p_i-1}
\;p_i-j\right)\,+\,1$ can have no prime factors greater than $p_i$,
hence $\left(\prod_{j=0}^{p_i-1} \;p_i-j\right)\,+\,1$ is a prime, and
it is greater than $p_i$, since $\prod_{j=0}^{p_i-1}\;p_i-j \ge p_i$.
This contradicts the maximality of $p_i$.  
Hence the assumption that
$p_i$ is the largest prime must be false, and so there is no largest
prime.

>>>>

\begin{center}
\large
\textbf{The Largest Prime}
\end{center}
\normalsize
\noindent
Suppose that there were a largest prime number $p$. 
Then consider the product $P = \prod_{i=1}^{p} \; i$. 
Then $P\,+\,1$ 
cannot be divided evenly by any of the numbers
up to $p$, $2,3,4,\ldots,p$ because each of these divides the left
factor evenly, but not the right factor, hence not their sum.
(Recall that if $a_1$ divides $a_2$ and $a_2=a_3+a_4$ then if $a_1$
divides $a_3$, it will also divide $a_4$.)  
Since we are assuming
$p$ is the largest prime,
$P\,+\,1$ can have no prime factors greater than $p$,
hence $P\,+\,1$ is a prime, and
it is greater than $p$, since $P \ge p$.
This contradicts the maximality of $p$.  
Hence the assumption that
$p$ is the largest prime must be false, and so there is no largest
prime.
